---
title: "M_0 and power"
output: html_document
---

Suppose that there are 50 pathogenic leaves. Assume independence among RVs, if a single test has the power of $\text{pw}$, to make sure that at least one of the 50 pathogenic leaves is identified at layer 1 with probability $0.99$, we need to set $(1-\text{pw})^{50} \leq 1-0.99$. Then we now that a single RV test needs to have the power at least 
```{r single-pwr}
 1-exp(log(1-0.99)/50)
```

```{r set-sample-szie}
# 1. set sample sizes and ratios
n1 <- 7504
n2 <- 2634
n <- n1+n2
xi1 <- n1/n
xi2 <- n2/n
```

Set the MAF in the control group. And then compute the odds ratio
```{r calculate-odds-ratio}
pi <- 1e-3  ## overal MAF
pi1 <- 8.28e-4 ## MAF in the control group
pi2 <- (pi - pi1*xi1)/xi2 ## MAF in the case group
pi2 
OR <- pi2*(1-pi1)/pi1/(1-pi2)
OR
```

Now we compute the signal-to-noise ratio

```{r set-d}
table.n<- c(pi*n1, (1-pi)*n1, pi*n2, (1-pi)*n2)
var.n <- sum(1/table.n)
var.n
table.a<- c(pi1*n1, (1-pi1)*n1, pi2*n2, (1-pi2)*n2)
var.a <- sum(1/table.a)
var.a
```
Then calculate the powre based on the two-sided $Z$-test. Here, $n$ is the leaf size.

```{r power}
library("pwr")
pwr.norm.test(d = log(OR)/sqrt(var.n),  n = 1:11, sig.level = 1e-4, alternative = "two.sided")
```